### 2021-04-21 preliminaries.tex
Briefly document GCN in Preliminaries
Resolves a comment from R2

\todo[inline,author=R2]{Why present only the feedforward NN in sect. 2.3 when you are using a GCN? You could at least include a paragraph about the main differences between these two models at the end of 2.3. Then 3.2 could focus on the aspects of GCN that are specific to this particular problem.}

>>>>

A \emph{\gls{gcn}} is a special case of feedforward \acrlong{nn}.
The modules of a \gls{gcn} transform messages that are passed along the edges of a graph encoded in the input example.
A particular architecture of a \gls{gcn} used prominently in this work is discussed in detail in \cref{sec:gcn}.
